workshop

### 2022-09-16 scripts/workshop/workshop.Rmd
update supp 1

```{r}
species_comp <- data %>% group_by(Species) %>% summarize(mean = mean(SQMean),
                                                         var = var(SQMean),
                                                         se = sqrt(var(SQMean)/n()))

species_comp %>% ggplot(.,aes(x=Species, y=mean)) + geom_point() + geom_linerange(aes(ymin=mean-se,ymax=mean+se))
```

>>>>

```{r}
species_comp <- data %>% group_by(Species) %>% summarize(mean = mean(SQMean),
                                                         var = var(SQMean),
                                                         se = sqrt(var(SQMean)/n()),
                                                         n = n()) %>% mutate(species_code = Species)

species_comp %<>% left_join(.,names)

species_comp %>% ggplot(.,aes(x=reorder(abb_name, mean), y=mean)) + geom_point() + geom_linerange(aes(ymin=mean-se,ymax=mean+se)) + theme(axis.text.x = element_text(angle = 30, hjust = 1))
